Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-28 manuscript.Rmd
Fix image rendering and update event counts

documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_word
output            : papaja::apa6_pdf
---

@@

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning System
[ICEWS; @DVN/28075_2015]. The event data were first filtered to remove
incomplete and incorrectly formatted data. They were then filtered to include
only events that were directed at (i.e., `target`) Syria ($n = INSERT NUMBER HERE$). To
explore the impact of outwardly directed Syrian events, the data were filtered
again to include events that were both directed at (i.e., `target`) or directed
by (i.e., `source`) Syria ($n = INSERT NUMBER HERE$).

@@

# read in social cohesion data
#cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")

@@

# calculate mean cohesion
raw_cohesion_data %>%
  group_by(date) %>%
  summarise(
    MeanCohesion = mean(Cohesion_avg),
    sd = sd(Cohesion_avg),
    var = sd^2,
    n = n(),
    se = sd / n) %>%
  ggplot(aes(x = date, y = MeanCohesion)) +
  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
#output            : papaja::apa6_pdf
---

@@

### Event Data
Event data were obtained from the 2012 Integrated Crisis Early Warning System
[ICEWS; @DVN/28075_2015]. The event data were first filtered to remove
incomplete and incorrectly formatted data. They were then filtered to include
only events that were directed at (i.e., `target`) Syria (n = `r num_target`). To
explore the impact of outwardly directed Syrian events, the data were filtered
again to include events that were both directed at (i.e., `target`) or directed
by (i.e., `source`) Syria (n = `r num_source_target`).

@@

# read in social cohesion data
raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")

@@

# calculate mean cohesion
raw_cohesion_ts <- raw_cohesion_data %>%
  group_by(date) %>%
  summarise(
    MeanCohesion = mean(Cohesion_avg),
    sd = sd(Cohesion_avg),
    var = sd^2,
    n = n(),
    se = sd / n) %>%
  ggplot(aes(x = date, y = MeanCohesion)) +
  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")

# save the plot
ggsave("./results/primary/raw-cohesion-ts.png")

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target - num_target` samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.
